\documentclass[a4paper,man,biblatex]{apa6}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber]{biblatex}
\usepackage[document]{ragged2e}
\setlength{\RaggedRightParindent}{0.5in}
\addbibresource{references.bib}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xpatch}
\xpatchbibdriver{online}
  {\printfield{entrysubtype}}
  {\printfield{entrysubtype}%
   \newunit\newblock
   \printfield{note}}
  {}
  {}

\renewcommand{\abstract}[1]{}

\title{The Rankability of Data}
\shorttitle{The Rankability of Data}
\author{Armant Touche}
\affiliation{Portland State University}
\date{\today}

\begin{document}
\thispagestyle{otherpage}
\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}

%\maketitle

\noindent Name: Armant Touche\newline
\noindent Date: 4/29/2020

\subsection{Description} I wanted to share an article on something I remember when I was high school around 2010. On the news, I can remember hearing that our oil reserve were predicted to be depleted by 2030 and have a peak around 2020. Marion King Hubbert in 1956 was scientist who worked at Shell lab and during his tenure there, he current the "Hubbert Curve" which predicted that oil depletion occur around 2000. His ideas were mostly forgotten and were update by two scientist in the 1980's which suggested the oil peak in global reserves would be peak between 2004-2005 which would be occur. Reduction in global of liquid hasn't occurred. The article I am sharing states that comparing absolutes are incompatible with mainstream views economic system. Apparently there is a lot to the oil industry being there are classification to oil. One classification being "conventional" and the others being "non-conventional." Crude oil is considered conventional oil. The common metric being used to help predict these peaks is million barrels used per day (Mb/d). Around 2008, the maximum value for oil usage was close to 100 Mb/d. The prediction was almost correct but was a little off other variables outside variables


\subsection{Why} 

\printbibliography

\end{document}
