\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}

\begin{document}
\title{\vspace{-2cm}Reflective Self-Evaluation}
\author{Armant Touche}
\maketitle

\begin{enumerate}

    \item Syllabus: The workload for this class was manageable because being consistent with putting in the work each day is key. I never took a hybrid class or self-driven pedagogical course before but nothing to crazy for me to handle. I didn't really have any expectations for this class because I am just trying to get through college and told I am required to take this class. I was surprised by how much I had to write but it was a pleasant surprise because I lack writing experience. I feel your expectation was right, given that a pandemic occurred. Thanks for being clear in your expectations of us and what we needed to do each week. I didn't have any hiccups so I feel I executed the workload well enough.

    \item Work Review: I really got some LaTex practice in. This was nice because I felt that doing any type of research in Microsoft Word or Google Docs can make a person distracted from the research because of formatting and citing sources accurately. Class sessions were not really engaging though because I felt a large part of the class didn't participate as much but given the current circumstances, I can understand not being fully present in class when life's constraints are constantly on one's mind. There weren't any obstacles for me participating with the class. I felt bad though when you asked a question and no one really responded. I can sense that this mode of teaching was hard for you and your TA but you two did great! 

    \item Prompts
    
    \begin{itemize}

        \item Attendance and Assignments: I had one unexcused absence because I was having roommate issues and I was distracted that day. I turned in all the assignments except for Syllabus Contract, which I thought I submitted but you were flexible and understanding with me. I would've like more feedback because I didn't understand the theme-requirement in the logs until a couple weeks into the course. When I received feedback on my first log, I felt confident that I did well on assignments.

        \item Reading and Class Discussion: A lot of reading was assigned but I read all the assigned reading and watched all the assigned videos. The logs were completed fully and turned in like we were instructed to do. I felt participated in class discussion a good amount. I felt inquiry log \#4 was my strongest since I had a better understanding.

        \item Research and Inquiry Project: I felt I put considerable amount of effort into my projects. Engaging other classmates was less fulfilling given the online nature of this class. I felt like I achieved a good result based on the feedback from other classmates. 

        \item Goals for learning: My research process received a lot of attention which I feel will help my in the future when conducting research. I wanted to get better at LaTex and this class really pushed to learn more about it.

        \item Takeaway: Learning how to CRAAP test is nice skill to have because I feel that research topics may have bias that stunt reproducibly but that is my opinion. PSU's inquiry is a nice approach to inter-disciplinary learning because overspecialization can less beneficial to the majority. Breaking down silo's and creating a more inclusive environment benefits everyone and not certain groups with special interests.

        \item Net Positives: I felt this course provided a lot reinforcement in certain views I have and introduced better one's like bio-diversity. I didn't come straight from high school to PSU and so I have a non-traditional view of the world and understand pre-conventional, conventional, and post-conventional ideas are present in a lot of life's aspects. 

        \item Class Review: I think the majority of students in our class had webcams but didn't choose to participate which is unfortunate. I wish classes were in person because I would be able to answer this prompt better. I felt if tried to engage other students more, it would be rude and I felt if I would've talk more, it would also be rude. I find it's better to listen more than talking. I am also an introvert so my natural tendency is to not talk that much anyway.

        \item My impact: I felt I had very little impact and I didn't want to be overzealous with participating.  

        \item Self-Grade (A-F): I believed I earned an \underline{\textbf{A}} because I was never late on submitting my assignments and did all the required assignments, reading, and I participated a considerable amount given the current circumstance. This makes feel uncomfortable not because of guilt or shame for not putting forth enough effort but because of lack of feedback. I still stand with giving myself an \underline{\textbf{A}}.

    \end{itemize}

\end{enumerate}


\end{document}
