\documentclass[a4paper,man,biblatex]{apa6}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber]{biblatex}
\usepackage[document]{ragged2e}
\setlength{\RaggedRightParindent}{0.5in}
\addbibresource{references.bib}
\usepackage{url}
\usepackage{xpatch}
\xpatchbibdriver{online}
  {\printfield{entrysubtype}}
  {\printfield{entrysubtype}%
   \newunit\newblock
   \printfield{note}}
  {}
  {}

\renewcommand{\abstract}[1]{}

\title{Inquiry Log \#3}
\shorttitle{Inquiry Log \#3}
\author{Armant Touche}
\affiliation{Portland State University}
\date{\today}

\begin{document}
\thispagestyle{otherpage}
\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}

%\maketitle

\noindent Name: Armant Touche\newline
\noindent Date: 4/29/2020

\subsection{Quotes}
%#1
\begin{enumerate}
    \item "Let nature never be forgot. Consult the genius of place in all." \autocite{dirtrich}
    \item "The carbon in the soil is like a cup of water, We have drunk more than half of it, but we can put more water back in the cup. With good soil practices, we could reverse global warming.” \autocite{soilsave}
    \item "The  same  way  acoustical  engineers  speak  of  “background  noise”  biologists talk about “background extinction.” In ordinary times— times here understood to mean whole geologic epochs— extinction takes place only very rarely, more rarely even than speciation, and it occurs at what’s known as the background extinction rate." \autocite{sixthsextinct} 

\end{enumerate}

\subsection{Observe} I again, choose my backyard as the setting for my observation period. I watched \textit{Dirt Rich} the previous night and had a thought how sometimes short-term goals obstruct any novel perspectives from being shared. But on that thought, I also wonder natural conservation efforts are implemented and how come data from any academic discipline's research isn't captivating a broader audience. But then again, being an individual is so easy because of all the possible distractions that a lot of people have access to. I am aware of my escapist tendencies and try to decompress in moderation because moderation is key for me to stay sane. I wish I could work for hours and days without the normal adult constraints which isn't the case. In my case, I set focus on long-term goals that would exponentially be beneficial. Developing this focus took a while to develop because of having a rough upbringing, I was not able to set long-term goals because of normal social pressures. As I mentioned in the beginning, short-term pleasures often blinded me from setting positive goals. The last couple of sentences were some ideas I was thinking about during my observation period.

\subsection{Reflect \& Theme} My theme for this inquiry log is in order to combat all the empirical evidences that is highlighting the decline in our environment is to be the solution. There is a semi-constant presence of eco-anxiety when discussing environment change. I categorize the anxiety as a helpless feeling because I am often connected to issue which to some degree is true. I have contributed my time to help alleviate this anxiety volunteering around 150 hours with Free Geek last year because I like their ethos and how the organization highlights the issue with the e-waste recycling. I don't understand why companies like Apple are still not held to a higher standard. Can't help having a negative bias towards Apple  and other major Tech companies. Tech companies unnecessary, constant output of new phones other appliances and the lack of ways to fix current or older products without resorting to their stores or a third party licensed repair shop.\\Fixing computers and teaching people how to fix and use their computers is something I've enjoyed. It was nice to be a part of organization that prided themselves on educating people about how to fixed their computers and learn about open source software. Allowing customers to fix their devices actually gives the consumer more economic power. Right now, I feel tech companies spend more money on how to make money when it should be invested on how to maintain and fix current technology. To re-iterate my theme for this log, I feel you have to be part of the solution. I wanted to fix computers and teach others how too. Steps like mine that help teach and give positive solution to modern problems could hopefully turn the tide in respects to the climate crisis which as of known, feels as though is reactive to the negative side-effects produced by humans.   

\subsection{Question}  What area of society can you see a solution being implemented that would help spread awareness? I have an issue with people who criticize government, whether the criticism is aimed at the local level or the federal level, and still not know the three branches of government \autocite{branchessurvey}. I think a lot knowledge can be gained through conscription which can either be combat related or non-combat related. Of course, you do not have to participate against your will but I believe there is some merit in participating in government role. I learned more about the structure of our government than I did in High school. Conscription would be open to all genders and creeds of course. Countries like Norway have conscription in place \autocite{norwayconscript}

\subsection{Words}  words

\printbibliography

\end{document}
