\documentclass[11pt,a4paper]{article} 
\usepackage{amssymb}
\usepackage[shortlabels]{enumitem}
\usepackage[fleqn]{amsmath} 
\usepackage{relsize}
\usepackage{graphicx}
\usepackage[super]{nth}
\usepackage{hyperref, url}
\usepackage[margin=2cm, top=2cm]{geometry}
\graphicspath{{./img/}}
\newcommand\setItemNumber[1]{\setcounter{enumi}{\numexpr#1-1\relax}}
\newcommand*{\mybox}[1]{\framebox{#1}}
\newcommand{\tuple}[1]{$\langle #1 \rangle$} 
\newcommand{\stuple}[1]{$\langle$#1$\rangle$} % ordered pair with strings inside
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

\title{\bf Homework 1\\[1ex]
\rm\normalsize CS250 Discrete Structures I, Winter 2020 }
\date{\normalsize Due: April 26, 2020}
\author{\normalsize Armant Touche}

\begin{document} 
\vspace{0cm}\maketitle 

	\paragraph{Chapter 3 Homework Exercises} For this week, you can complete many of the exercises in 3.1 using truth tables. Alternatively, if you know some rules of logic, you can make use of those. Section 3.2 is a bit more conceptual in nature, covering proof strategies at an abstract level.
	
	\subparagraph{Problem 1} 3.1 Propositional Logic (pg. 209-212) \\
			
		From section 3.1 in the textbook, complete exercises 1, 3, 6, 9, 10, 14

    \begin{enumerate}

        %1
        \item Consider the statement about a party, “If it’s your birthday or there will be cake, then there will be cake.”
            \begin{enumerate}
                \item Translate the above statement into symbols. Clearly state which statement is $P$ and which is $Q$.
                \item Make a truth table for the statement.
                \item Assuming the statement is true, what (if anything) can you conclude if there will be cake?
                \item Assuming the statement is true, what (if anything) can you conclude if there will not be cake?
                \item Suppose you found out that the statement was a lie. What can you conclude?
            \end{enumerate}

        %3

        %6



    \end{enumerate}
	
	\subparagraph{Problem 2} 3.2 Proofs (pg. 223-226) \\
	
		From section 3.2 in the textbook, complete exercises 1, 2, 6, 10.



\end{document}
