\documentclass{letter}
\usepackage{hyperref}
\signature{Armant Touche}
\begin{document}

\begin{letter}{Name: Armant Touche \\ Class: CS 250 
\\ }
\opening{To David Lu,}

Appreciate your openness to feedback. In this letter I will be answering the following:\\\\
1. How's this class going?  What am I doing that's going well?  What can I do to better support you in this class\\\\
The is class is going I guess. It's hard to learn without the normal feedback that is provided in in-person classes. You are super understanding and just want us to learn which alleviates some stress. I have no input on what could be done better but I think just being supportive is good enough, which is what you are doing. Keep it up!\\\\
2. How are your other classes going?  What are your other professors doing well that I might learn from?\\\\
I am taking three other classes and they're going fine. I am little burnt out but I cannot complain. Other professors aren't doing anything too different from you.\\\\
3. Is there anything you're struggling with logistical?\\\\
I am not struggling at the moment.\\\\
4. What are some pros and cons of the online format for you, now that you have some experience with it?  What about asynchronous vs synchronous teaching?\\\\
Like I mention in the first answer, the lack of feedback that comes from in-person meetings is a con. The plus is that with asynchronous learning, I am able to learn on my own and come with prepared questions. I prefer self-learning and then receiving input on what to focus on.\\\\
5. How do you feel about self-learning?  What's working for you?  What are the challenges?\\\\
I prefer self-learning because learning usually feels like drinking water from a fire hydrant. Being able to self learn works for me but still, there is the feedback challenge.\\\\
6. Are there any topics we've covered that are particularly interesting or are related to other computing problems you've worked on?\\\\
I am interested in sequence section of the book and binary relations.\\\\
7.  Which topics  were  particularly  challenging  for  you  where  you  could  use  some  further study and practice?\\\\
The binary relation because of how abstract it is. Sorry I was short in my feedback but I am actually a little stressed. Thank you for teaching.


\closing{Thanks for reading David,}

\end{letter}
\end{document}
